### 2018-07-11 submission/manuscript.Rmd
add disclaimer to abstract that effect needs to match fecal samples

**Conclusions.** Although there are 16S rRNA gene sequencing differences based on polymerase and number of cycles used, they are small with respect to the biological differences between indivdiuals. Collectively, these results provide evidence that a real biological difference between groups, based on 16S rRNA gene sequencing, should be detectable regardless of polymerase and number of cycles used.

>>>>

**Conclusions.** Although there are 16S rRNA gene sequencing differences based on polymerase and number of cycles used, they are small with respect to the biological differences between fecal bacterial communities within indivdiuals. Collectively, these results provide evidence that a real biological difference between groups, based on 16S rRNA gene sequencing of fecal samples, should be detectable regardless of polymerase and number of cycles used.

### 2018-07-11 submission/manuscript.tex
add disclaimer to abstract that effect needs to match fecal samples

\textbf{Conclusions.} Although there are 16S rRNA gene sequencing
differences based on polymerase and number of cycles used, they are
small with respect to the biological differences between indivdiuals.
Collectively, these results provide evidence that a real biological
difference between groups, based on 16S rRNA gene sequencing, should be
detectable regardless of polymerase and number of cycles used.

>>>>

\textbf{Conclusions.} Although there are 16S rRNA gene sequencing
differences based on polymerase and number of cycles used, they are
small with respect to the biological differences between fecal bacterial
communities within indivdiuals. Collectively, these results provide
evidence that a real biological difference between groups, based on 16S
rRNA gene sequencing of fecal samples, should be detectable regardless
of polymerase and number of cycles used.
